A Fast Unified Model for Parsing and Sentence Understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Remove induced redundancy.

We propose an alternative space-efficient stack representation inspired by the zipper technique \citep{huet1997zipper}, that we call \textit{thin stack}. For each input sentence, we represent the stack with a single $T \times D$ matrix $S$. Each row $S_t$ represents the top of the actual stack at timestep $t$. We maintain a queue of backpointers onto $S$ that indicates which elements would be involved in a \reduce\ operation at any given step. The thin stack algorithm (Algorithm~\ref{alg:thin-stack}) describes the full mechanics of a stack feedforward in this compressed representation. It operates on the compressed $T \times D$ matrix $S$ and a backpointer queue $Q$. Table~\ref{tbl:thin-stack} shows a sample run.

>>>>

We propose an alternative space-efficient stack representation inspired by the zipper technique \citep{huet1997zipper}, that we call \textit{thin stack}. For each input sentence, we represent the stack with a single $T \times D$ matrix $S$. Each row $S_t$ represents the top of the actual stack at timestep $t$. We maintain a queue of backpointers onto $S$ that indicates which elements would be involved in a \reduce\ operation at any given step. Algorithm~\ref{alg:thin-stack} describes the full mechanics of a stack feedforward in this compressed representation. It operates on the compressed $T \times D$ matrix $S$ and a backpointer queue $Q$. Table~\ref{tbl:thin-stack} shows an example run.
